Trends of SDR in Thessaloniki

### 2023-08-31 Article.Rmd
Commit 2023-08-31 19:10

<!-- \footnotesize -->
```{r trendtable, echo=F}
LT <- data.table(read.csv("./figures/tbl_longterm_trends.dat",
               strip.white = TRUE,
               sep = ";",
               header = TRUE))
LT <- LT[grep("SDR", LT$var), ]
LT$slope.sd           <- NULL
LT$slope.ConfInt_0.95 <- NULL
LT$slope.ConfInt_0.99 <- NULL
LT$var                <- NULL
setorder(LT, -slope.stat_sig)
rownames(LT) <- NULL
names(LT)    <- c("Trend [%/year]", "Trend p-value", "Sky condition", "Trend statistical signif. [%]")
## no need all are 100%
LT$`Trend statistical signif. [%]` <- NULL

@@

Similar we have produced the deseasonalized trend for different sky conditions for each season of the year, using the corresponding mean monthly values.
This can give us a better understanding of the annual variability of the trends.

@@

<!-- \footnotesize -->
```{r trendseasontable, echo=F}
pp <- read.csv("./figures/tbl_longterm_trends_season.dat",
               strip.white = TRUE,
               sep = ";",
               header = TRUE)
pp <- pp[grep("SDR" ,pp$var), ]
pp$slope.sd           <- NULL
pp$slope.ConfInt_0.95 <- NULL
pp$slope.ConfInt_0.99 <- NULL
pp$var                <- NULL
rownames(pp) <- NULL
names(pp) <- c("Trend [%/year]", "Trend p-value", "Sky condition", "Season", "Trend statistical signif. [%]")

# panderOptions("table.alignment.default", "left")
panderOptions("table.alignment.default", "center")
pander(pp,
       caption = "\\label{tab:trendseasontable}Trends of daily means by sky conditions for the seasons of the year.")
```
<!-- \normalsize -->

>>>>

<!-- \footnotesize -->
```{r trendtable, echo=F}
LT <- data.table(read.csv("./figures/tbl_longterm_trends.dat",
               strip.white = TRUE,
               sep = ";",
               header = TRUE))
LT <- LT[grep("SDR", LT$var), ]
LT$slope.sd           <- NULL
LT$slope.ConfInt_0.95 <- NULL
LT$slope.ConfInt_0.99 <- NULL
LT$var                <- NULL
setorder(LT, -slope.stat_sig)
rownames(LT) <- NULL
names(LT)    <- c("Trend [%/year]", "Trend p-value", "Sky condition", "Trend statistical signif. [%]")
## no need all are 100%
LT$`Trend statistical signif. [%]` <- NULL
## numeric presision
LT$`Trend [%/year]` <- signif(LT$`Trend [%/year]`, 3)
LT$`Trend p-value`  <- signif(LT$`Trend p-value`,  3)

@@

Similar to the long term trends discussed above, we have produced the deseasonalized trend for the different sky conditions, for each season of the year, using the corresponding mean monthly values.

This can give us a better understanding of the annual cycle of the trends.

@@

<!-- \footnotesize -->
```{r trendseasontable, echo=F}
pp <- read.csv("./figures/tbl_longterm_trends_season.dat",
               strip.white = TRUE,
               sep = ";",
               header = TRUE)
pp <- pp[grep("SDR" ,pp$var), ]
pp$slope.sd           <- NULL
pp$slope.ConfInt_0.95 <- NULL
pp$slope.ConfInt_0.99 <- NULL
pp$var                <- NULL
rownames(pp)          <- NULL
names(pp) <- c("Trend [%/year]", "Trend p-value", "Sky condition", "Season", "Trend statistical signif. [%]")
## order by season
target    <- c("Winter", "Spring", "Summer", "Autumn")
new_order <- sapply(target, function(x,pp){which(pp$Season == x)}, pp=pp)
pp        <- pp[new_order,]
## numeric precision
pp$`Trend [%/year]` <- signif(pp$`Trend [%/year]`, 3)
pp$`Trend p-value`  <- signif(pp$`Trend p-value`,  3)

rownames(pp) <- NULL

# panderOptions("table.alignment.default", "left")
panderOptions("table.alignment.default", "center")
pander(pp,
       caption = "\\label{tab:trendseasontable}SDR trends of monthly anomaly for each season of the year. The vertical scale is common for all subplots, for easier comparison.")
```
<!-- \normalsize -->
